Title here

### 2020-07-10 paper/paper.Rmd
modify notation as per wednesday meeting (16)

The optimisation problem we're interested in is in the context of projection pursuit. Coined by @friedman1974projection, projection pursuit is a method that detects the interesting structure (i.e. clustering, outliers and skewness) of multivariate data via projecting it in lower dimensions. Let $\mathbf{D}_{n \times p}$ be a data matrix, an n-d projection can be seen as a linear transformation: $T: \mathbb{R}^p \mapsto \mathbb{R}^d$ defined by $\mathbf{P} = \mathbf{D} \cdot \mathbf{A}$, where $\mathbf{P}_{n \times p}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection basis  Define $f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}$ be an index function that maps the projection basis $\mathbf{A}$ onto a scalar value $I$, this function is commonly known as the projection pursuit index (PPI) function, or index function and can be used to measure the "interestingness" of the projection. A number of indice functions have been proposed in the literature and this includes Legendre index [@friedman1974projection], hermite index [@hall1989polynomial], natural hermite index [@cook1993projection], chi-square index [@posse1995projection], LDA index [@lee2005projection] and PDA index [@lee2010projection]. [Any literature on holes index? xxx]

@@

\begin{align}
&\arg \max_{\mathbf{A} \in \mathcal{A}} f(\mathbf{A}) \\
s.t. & \mathcal{A} = \{ \forall \mathbf{a}_i \in \mathbf{A}: \lVert \mathbf{a}_i \rVert = 1 \}
\end{align}

via an iterative search: $\{\mathbf{A}^j: \mathbf{A}^1, \mathbf{A}^2, \cdots \cdots \mathbf{A}^J\}$. Guided tour interpolates geodesically between each basis found by projection pursuit $A^j$ to form a tour path: $$\{ \mathbf{A}^0, \mathbf{A}^1, {}_{1}\mathbf{A}^1, {}_{2}\mathbf{A}^1,\cdots, {}_{k_1}\mathbf{A}^1, A^2, {}_{1}\mathbf{A}^2, {}_{2}\mathbf{A}^2, \cdots {}_{k_2}\mathbf{A}^2, \cdots, \mathbf{A}^{J-1}, {}_{1}\mathbf{A}^{J-1}, \cdots {}_{k_m}\mathbf{A}^{J-1} ,\mathbf{A}^J \}$$

@@

Now we formulate the idea of global object using mathmetical notation. Let $\mathbf{A}^0$ denotes the starting basis. Superscript $j$ is used to denote the number of iteration (index per iteration). Candidate basis are denoted using subscript on the right and interpolation basis are denoted using subscript on the left.  For example, $\mathbf{A}^1_{2}$ means the second candidate basis in the first iteration and ${}_{2}\mathbf{A}^1$ means the second interpolation basis that forms the tour path from the current basis $\mathbf{A}^0$ to the target basis $\mathbf{A}^1$. In iteration two, $\mathbf{A}^1$ becomes the current basis and projection pursuit searches through $\mathbf{A}^2_{1}, \mathbf{A}^2_{2}, \cdots, \mathbf{A}^2_{l_2}$ to find the target basis $\mathbf{A}^2$. The tour path from $\mathbf{A}^1$ to $\mathbf{A}^2$ is constructed using the interpolation bases ${}_{1}\mathbf{A}^2, {}_{2}\mathbf{A}^2, \cdots, {}_{k_2}\mathbf{A}^2$. All the bases together can be arranged in a format that each coloumn represents an iteration as in Equation \ref{eq:matrixA}.

\begin{equation}
\left[
\begin{array}{ccccccc}
/ & \mathbf{A}^1_1 & \mathbf{A}^2_1 & \cdots & \mathbf{A}^j_1 &\cdots & \mathbf{A}^J_1 \\
/ & \mathbf{A}^1_2 & \mathbf{A}^2_2 & \cdots & \mathbf{A}^j_2 &\cdots & \mathbf{A}^J_2 \\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
/ &\mathbf{A}^1_{l_1} & \mathbf{A}^2_{l_2} & \cdots & \mathbf{A}^j_{l_h} &\cdots & \mathbf{A}^J_{L_H}\\
\hline
\mathbf{A}^0 & \mathbf{A}^1 & \mathbf{A}^2 & \cdots & \mathbf{A}^j  &\cdots & \mathbf{A}^J\\
\hline
/ &{}_{1}\mathbf{A}^1 & {}_{1}\mathbf{A}^2 & \cdots &{}_{1}\mathbf{A}^j & \cdots & /\\
/ &{}_{2}\mathbf{A}^1 & {}_{2}\mathbf{A}^2 & \cdots &{}_{2}\mathbf{A}^j & \cdots & / \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & / \\
/ &{}_{k_1}\mathbf{A}^1 & {}_{k_2}\mathbf{A}^2 & \cdots &{}_{k_m}\mathbf{A}^j & \cdots & / \\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\vphantom{A^J_1}\text{candidate basis} \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_{L_H}}\text{candidate basis} \\
\hline
\vphantom{A^J}\text{output basis} \\
\hline
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\end{array}
\right]
\label{eq:matrixA}
\end{equation}

@@

\begin{equation}
\begin{bsmallmatrix}
\mathbf{A}^0 &\mathbf{A}^1_1 &  \mathbf{A}^1_{2} & \cdots& \mathbf{A}^1_{l_1} & \mathbf{A}^1 & {}_{1}\mathbf{A}^1& {}_{2}\mathbf{A}^1 &\cdots& {}_{k_1}\mathbf{A}^1 & \mathbf{A}^2_1 & \mathbf{A}^2_{2} & \cdots& \mathbf{A}^2_{l_2} & \mathbf{A}^2 & {}_{1}\mathbf{A}^2 &{}_{2}\mathbf{A}^2 &\cdots& {}_{k_2}\mathbf{A}^2 & \cdots & \mathbf{A}^J
\end{bsmallmatrix} 
\label{eq:vectorA}
\end{equation}

\begin{equation}
\left[
\begin{array}{c|c|ccc|ccc}
\mathbf{A}^0 & I^0 & 0 & / & 1 & / & \cdots & /\\
\hline
\mathbf{A}^1_1 & I^1_1 & 1 & 1 & 2 & o_{1, 1} & \cdots & o_{p, 1}\\
\mathbf{A}^1_2 & I^1_2 & 1 & 2 & 3 & o_{1, 2} & \cdots & o_{p, 2}\\
\vdots &\vdots & \vdots &\vdots &\vdots &\vdots &\cdots &\vdots\\
\mathbf{A}^1_{l_1} & I^1_{l_1} & 1 & l_1 & l_1+1 & \vdots & \cdots & \vdots\\
\hline 
\mathbf{A}^1 & I^1 & 1 & l_1 + 1 & l_1 + 2 & \vdots & \cdots & \vdots\\
\hline
{}_{1}\mathbf{A}^1 &{}_{1}I^1 & 1 & / & l_1 + 3 &\vdots & \cdots & \vdots\\
{}_{2}\mathbf{A}^1 &{}_{2}I^1 & 1 & / & l_1 + 4&\vdots & \cdots & \vdots\\
\vdots &\vdots &\vdots  &\vdots &\vdots &\vdots &\cdots &\vdots \\
{}_{k_1}\mathbf{A}^1 &{}_{k_1}I^1 & 1 & / & l_1 +k_1 + 2 &\vdots & \cdots & \vdots\\
\hline
\vdots &\vdots &\vdots  &\vdots &\vdots &\vdots &\cdots &\vdots \\
\mathbf{A}^J_{l_H} & I^J_{l_H} & J & l_H & n-1 &o_{1, n-1}& \cdots & o_{p, n-1}\\
\mathbf{A}^J & I^J & J & l_H + 1 & n & o_{1, n}& \cdots & o_{p, n}\\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}

where $n = (J-1) + \sum_{h = 1}^H l_h + \sum_{m = 1}^M k_m + 1$

>>>>

The optimisation problem we're interested in is in the context of projection pursuit. Coined by @friedman1974projection, projection pursuit is a method that detects the interesting structure (i.e. clustering, outliers and skewness) of multivariate data via projecting it in lower dimensions. Let $\mathbf{X}_{n \times p}$ be a data matrix, an n-d projection can be seen as a linear transformation: $T: \mathbb{R}^p \mapsto \mathbb{R}^d$ defined by $\mathbf{P} = \mathbf{X} \cdot \mathbf{A}$, where $\mathbf{P}_{n \times p}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection basis  Define $f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}$ be an index function that maps the projection basis $\mathbf{A}$ onto a scalar value $I$, this function is commonly known as the projection pursuit index (PPI) function, or index function and can be used to measure the "interestingness" of the projection. A number of indice functions have been proposed in the literature and this includes Legendre index [@friedman1974projection], hermite index [@hall1989polynomial], natural hermite index [@cook1993projection], chi-square index [@posse1995projection], LDA index [@lee2005projection] and PDA index [@lee2010projection]. [Any literature on holes index? xxx]

@@

\begin{align}
&\arg \max_{\mathbf{A} \in \mathcal{A}} f(\mathbf{A}) \\
s.t. & \mathcal{A} = \{ \forall \mathbf{a}_i, \mathbf{a}_j \in \mathbf{A}: \lVert \mathbf{a}_i \rVert = 1 \text{ and } \mathbf{a}_i \mathbf{a}_j = 0 \}
\end{align}

via an iterative search: $\{\mathbf{A}^1, \mathbf{A}^2, \cdots \cdots \mathbf{A}^J\}$. Guided tour interpolates geodesically between each basis found by projection pursuit $A^j$ to form a tour path: $$\{ \mathbf{A}^0, \mathbf{A}^1, {}_{1}\mathbf{A}^1, {}_{2}\mathbf{A}^1,\cdots, {}_{k_1}\mathbf{A}^1, A^2, {}_{1}\mathbf{A}^2, {}_{2}\mathbf{A}^2, \cdots {}_{k_2}\mathbf{A}^2, \cdots, \mathbf{A}^{J-1}, {}_{1}\mathbf{A}^{J-1}, \cdots {}_{k_m}\mathbf{A}^{J-1} ,\mathbf{A}^J \}$$

@@

Now we formulate the idea of global object using mathmetical notation. Let $$\mathbf{A}_{j,l,k}$$ denotes the projection matrix in iteration $j$. If it is searching basis produced in the optimisation, then it has a subscript $l$. If it is an interpolation basis, it has a $k$ subscript. For example $\mathbf{A}_{1,2,/}$ means the second searching basis in the first iteration, $\mathbf{A}_{1, /, 2}$ means the second interpolation basis that on the tour path from the current basis $\mathbf{A}^0$ to the target basis found in iteration 1: $\mathbf{A}^1$. The target basis found in each iteration, $\mathbf{A}_{j, l_j, /}$ can also be simplified using a superscript as $\mathbf{A}^j$.

Let $\mathbf{A}^0$ denotes the starting basis. Superscript $j$ is used to denote the number of iteration (index per iteration). Candidate basis are denoted using subscript on the right and interpolation basis are denoted using subscript on the left.  For example, $\mathbf{A}^1_{2}$ means the second candidate basis in the first iteration and ${}_{2}\mathbf{A}^1$ means the second interpolation basis that forms the tour path from the current basis $\mathbf{A}^0$ to the target basis $\mathbf{A}^1$. In iteration two, $\mathbf{A}^1$ becomes the current basis and projection pursuit searches through $\mathbf{A}^2_{1}, \mathbf{A}^2_{2}, \cdots, \mathbf{A}^2_{l_2}$ to find the target basis $\mathbf{A}^2$. The tour path from $\mathbf{A}^1$ to $\mathbf{A}^2$ is constructed using the interpolation bases ${}_{1}\mathbf{A}^2, {}_{2}\mathbf{A}^2, \cdots, {}_{k_2}\mathbf{A}^2$. All the bases together can be arranged in a format that each coloumn represents an iteration as in Equation \ref{eq:matrixA}.

\begin{equation}
\left[
\begin{array}{ccccccc}
\ast & \mathbf{A}_{1,1,\ast} & \mathbf{A}_{2, l_1 +1,\ast} & \cdots & \mathbf{A}_{j,\sum_{i = 1}^{j-1}l_i +1,\ast} &\cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +1 ,\ast} \\
\ast & \mathbf{A}_{1,2,\ast} & \mathbf{A}_{2,l_1 +2,\ast} & \cdots & \mathbf{A}_{j,\sum_{i = 1}^{j-1}l_i +2,\ast} &\cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +2, \ast} \\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
\ast & \mathbf{A}_{1, l, \ast} & \mathbf{A}_{2, l_1 + l, \ast} & \cdots & \mathbf{A}_{j, \sum_{i = 1}^{j-1}l_i + l, \ast}  &\cdots & \mathbf{A}_{J, \sum_{i = 1}^{J-1}l_i + l, \ast}\\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
\mathbf{A}_{0,\ast,\ast} & \mathbf{A}_{1, l_1, \ast} & \mathbf{A}_{2, l_1 + l_2, \ast} & \cdots & \mathbf{A}_{j, \sum_{i = 1}^{j}l_i , \ast}  &\cdots & \mathbf{A}_{J, \sum_{i = 1}^{J} l_i, \ast}\\
\hline
\ast &\mathbf{A}_{1, \ast, 1} & \mathbf{A}_{2, \ast, k_1 + 1} & \cdots &\mathbf{A}_{j, \ast,\sum_{i = 1}^{j-1}k_i + 1} & \cdots & \ast\\
\ast &\mathbf{A}_{1, \ast, 2} & \mathbf{A}_{2, \ast, k_1 + 2} & \cdots &\mathbf{A}_{j, \ast, \sum_{i = 1}^{j-1}k_i +2} & \cdots & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k} & \mathbf{A}_{2, \ast, k_1 + k} & \cdots &\mathbf{A}_{j, \ast, \sum_{i = 1}^{j-1}k_i +k} & \cdots & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k_1} & \mathbf{A}_{2, \ast, k_1 + k_2} & \cdots &\mathbf{A}_{j, \ast,\sum_{i = 1}^{j}k_i} & \cdots & \ast \\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\vphantom{A^J_1}\text{candidate basis} \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J}\text{current/target basis} \\
\hline
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\end{array}
\right]
\label{matrixA}
\end{equation}

@@

All the basis can also be denoted usign a single subscript by their natural ordering as $\mathbf{A}_0, \mathbf{A}_1, \cdots, \mathbf{A}_n$.

\begin{equation}
\begin{array}{cccccccc}
\bigl[\mathbf{A}_{0, \ast, \ast} & 
\mathbf{A}_{1, 1, \ast} & 
\mathbf{A}_{1,2,\ast} & 
\cdots & 
\mathbf{A}_{1,l,\ast} & 
\cdots & 
\mathbf{A}_{1,l_1, \ast}   \\ 
\mathbf{A}_{1, \ast, 1} & 
\mathbf{A}_{1, \ast, 2} & 
\cdots &
\mathbf{A}_{1, \ast, k} &
\cdots &
\mathbf{A}_{1, \ast, k_1} &
\cdots &
\mathbf{A}_{J, l_J, \ast} \bigr]
\end{array} 
\label{eq:vectorA}
\end{equation}

\begin{equation}
\left[
\begin{array}{c|c|cccc|ccc}
\mathbf{A} & I & j &  l  & k & n & S_{1}& \cdots & S_{p}\\
\hline
\mathbf{A}_0 & I_0 & 0 & \ast & \ast & 1 & \ast & \cdots & \ast\\
\hline
\mathbf{A}_1 & I_1 & 1 & 1 & \ast& 2 & S_{1, 1} & \cdots & S_{p, 1}\\
\mathbf{A}_2 & I_2 & 1 & 2 &\ast & 3 & S_{1, 2} & \cdots & S_{p, 2}\\
\vdots &\vdots & \vdots &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots\\
\vdots & \vdots & 1 & l_1 & \ast & \vdots & \vdots & \cdots & \vdots\\
\hline
\vdots & \vdots & 1 & \ast & 1& \vdots &\vdots & \cdots & \vdots\\
\vdots &\vdots& 1 & \ast & 2& \vdots&\vdots & \cdots & \vdots\\
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\vdots &\vdots & 1 & \ast & k_1&\vdots &\vdots & \cdots & \vdots\\
\hline
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\mathbf{A}_n & I_n & J &  l_J & \ast & n & S_{1, n}& \cdots & S_{p, n}\\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}

where $n = 1+ \sum_{i = 1}^J l_i + \sum_{i = 1}^{J-1} k_i$
